---
title: "DATA 607 TidyVerse Create Assignment"
author: "Susanna Wong"
date: "2023-04-05"
output:
  html_document:
    theme: cerulean
    # code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment Prompt

In this assignment, you'll practice collaborating around a code project with GitHub.
You could consider our collective work as building out a book of examples on how to use TidyVerse functions.
GitHub repository: <https://github.com/acatlin/SPRING2023TIDYVERSE> FiveThirtyEight.com datasets.
Kaggle datasets.

Your task here is to Create an Example.
Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample "vignette" that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset.
(25 points)

Later, you'll be asked to extend an existing vignette.
Using one of your classmate's examples (as created above), you'll then extend his or her example with additional annotated code.
(15 points)

You should clone the provided repository.
Once you have code to submit, you should make a pull request on the shared repository.
You should also update the README.md file with your example.
After you've created your vignette, please submit your GitHub handle name in the submission link provided below.
This will let your instructor know that your work is ready to be peer-graded.

# Packages

The `tidyverse` package is a collection of packages that includes `ggplot2`, `dplyr`, `tidyr`, `readr`, `purr`, `tibble`, `stringr`, `forcats`.

For this assignment, we will be using the following packages.

| Package   | Function                                                      |
|------------------|------------------------------------------------------|
| `readr`   | `read.csv`                                                    |
| `dplyr`   | `glimpse` `group_by()` `summarise()` `mutate()`               |
| `ggplot2` | `ggplot` `geom_bar` `scale_x_continuous()` `labs()` `ggtitle` |
| `scales`  | `percent()`                                                   |
| `DT`      | `datatable()`                                                 |

# Dataset

from FiveThirtyEight,

# Load data

The data is in store in a csv file that can be found here.

Use `read.csv` from `readr` package to read the csv file as a dataframe.
Use `<-` to store the data as a variable in R.
Below, we store the data as `raw_data`.
You can use `glimpse()` from `dplyr` package to get a glimpse of the data.

```{r, message=FALSE}
raw_data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")

library(DT)
datatable(raw_data, options = list(scrollX = TRUE))
```

# Question 1: Which major category has the highest share of women? {.tabset}

## Analysis

In the `raw_data`, there are detailed information for each of the 173 majors.
In order to answer the question, we need to group the major category, and find the total people, total women, and total men for each major category.

It seems that the `raw_data` is already tidied.
We should create a new dataframe for our analysis and make no changes to the `raw_data`.

Use `%>%` from the `magrittr` package to pipe the `raw_data` into our new dataframe, `college_major`.

    college_major <- raw_data %>%

Next, use `group_by()` function from the `dplyr` package to group rows by column value, `Major_category`.

    college_major <- raw_data %>%
      group_by(Major_category) %>%

Then, use `summarise()` and `sum()` functions to sum by group.
We find the total women, total men, and total people for each major category.

    college_major <- raw_data %>%
      group_by(Major_category) %>% #Here we group the major category
      summarise(Total = sum(Total,na.rm=TRUE), 
        Men = sum(Men,na.rm=TRUE), 
        Women = sum(Women,na.rm=TRUE)) %>%

By now, we should have the total women, total men, and total people for each major category.
Use `mutate()` from the `dplyr` package to create a new column for the percentage of women for each major category.
Use `na.rm=TRUE` to exclude NA's.
Otherwise, the NA will be return if there is a NA value for the major category.

```{r, message=FALSE}
# install.packages('dplyr')
library(dplyr)
# install.packages('ggplot2')
library(ggplot2)

college_major <- raw_data %>%
  group_by(Major_category) %>% #Here we group the major category
  summarise(Total = sum(Total,na.rm=TRUE), 
            Men = sum(Men,na.rm=TRUE), 
            Women = sum(Women,na.rm=TRUE)) %>% # We find the total women, total men, and total people for each major category. 
  mutate(ShareWomen = Women/Total)
```

```{r}
datatable(college_major, options = list(scrollX = TRUE), caption = 'Table 1: This is raw_data from FiveThirtyEight. It contains the number of recent grads for each major, the type of jobs they got, and more')
```

## Visualization

Use `ggplot` to graph the dataframe.
Use `reorder()` function to reorder the major category by the percentage of women.

The code below will reorder the `Major_category` by the percentage of women from highest to lowest.

```{r}
ggplot(data = college_major, aes(y = reorder(Major_category, ShareWomen), x = ShareWomen)) + geom_bar(stat="identity")  
```

The code below will reorder the `Major_category` by the percentage of women from lowest to highest.

```{r}
ggplot(data = college_major, aes(y = reorder(Major_category, -ShareWomen), x = ShareWomen)) + geom_bar(stat="identity")  
```

Rename the axes label using `labs()`.
Add a title for the bar graph using `ggtitle()`.
Use `scale_x_continuous()` from `ggplot2` package and `percent()` from `scales` package to include percentage in the x-axis.

```{r}
ggplot(data = college_major, aes(y = reorder(Major_category, ShareWomen), x = ShareWomen)) + geom_bar(stat="identity")  +  labs(x = "Percentage of Women" , y = "Major Category") + ggtitle("Percentage of Women in Each Major Category") + scale_x_continuous(labels = scales::percent) 
```

# Source

<https://www.tidyverse.org/packages/>

<https://dplyr.tidyverse.org/reference/index.html>

<https://ggplot2.tidyverse.org/reference/>
