---
title: "college major"
author: "Susanna Wong"
date: "2023-04-05"
output:
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment Prompt

In this assignment, you'll practice collaborating around a code project with GitHub. You could consider our collective work as building out a book of examples on how to use TidyVerse functions. GitHub repository: <https://github.com/acatlin/SPRING2023TIDYVERSE> FiveThirtyEight.com datasets. Kaggle datasets.

Your task here is to Create an Example. Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample "vignette" that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. (25 points)

Later, you'll be asked to extend an existing vignette. Using one of your classmate's examples (as created above), you'll then extend his or her example with additional annotated code. (15 points)

You should clone the provided repository. Once you have code to submit, you should make a pull request on the shared repository. You should also update the README.md file with your example. After you've created your vignette, please submit your GitHub handle name in the submission link provided below. This will let your instructor know that your work is ready to be peer-graded. 

# Dataset 

# Load data

The data is in store in a csv file that can be found here. 

`read.csv` will read the csv file as a dataframe. Use `<-` to store the data as a variable in R. Below, we store the data as `raw_data`.

```{r}
raw_data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")
```

# Which major category has the highest share of women? {.tabset}


```{r pressure, echo=FALSE}
library(dplyr)
# install.packages('ggplot2')
library(ggplot2)
# college_major <- raw_data %>%
#   group_by(Major_category) %>%
#   summarise(total = sum(Total,na.rm=TRUE), Men = sum(Men,na.rm=TRUE), Women = sum(Women,na.rm=TRUE), Employed = sum(Employed, na.rm=TRUE), Full_time = sum(Full_time, na.rm=TRUE), Part_time = sum(Part_time, na.rm=TRUE), Full_time_year_round = sum(Full_time_year_round, na.rm=TRUE), Unemployed = sum(Unemployed, na.rm=TRUE), College_jobs = sum(College_jobs, na.rm=TRUE), Non_college_jobs = sum(Non_college_jobs,na.rm=TRUE), Low_wage_jobs = sum(Low_wage_jobs, na.rm=TRUE))

college_major <- raw_data %>%
  group_by(Major_category) %>%
  summarise(Total = sum(Total,na.rm=TRUE), Men = sum(Men,na.rm=TRUE), Women = sum(Women,na.rm=TRUE)) %>%
  mutate(ShareWomen = Women/Total)

```

```{r}
ggplot(data = college_major, aes(x = reorder(Major_category, ShareWomen), y = ShareWomen)) + geom_bar(stat="identity") + coord_flip() + 
```


 